Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-25 paper/aldebaran.tex
text about gamma dra

The stellar oscillations are best fit with a single, low-quality ($Q =
\CombinedQRange{}$) oscillatory mode with $\numax = 2.238^{+ 0.086}_{- 0.080}$
\muHz.  We find no improvement in the marginal likelihood (evidence) or other
model-selection information criteria \citep{Gelman2013} from models with
additional oscillatory modes, so we conclude that the large spacing $\Delta\nu$
is not observable in this data set.  We have determined the stellar properties
of Aldebaran with the additional constraint of \numax determined from this
analysis.  The details of the stellar modelling are presented in Appendix
\ref{sec:mod}.  We have considered the impact of our additional \numax
constraint and run our analysis for different sets of spectroscopic estimates.
For final values we adopt the \citet{2012Sheffield} spectroscopic solution as
being `middle of the road' estimates.  For the analysis without constraint on
\numax we find estimates of the stellar properties as $M = 1.27^{+0.24}_{-0.2}
\, \mathrm{M_{\odot}}$ and age $4.86^{+3.56}_{-2.04} \, \rm Gyr$.  With the
inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and
age $6.38^{+1.42}_{-1.12} \, \rm Gyr$.  It is clear that the addition of \numax
provides substantially more precise estimates of mass and age. With this stellar
mass, the radial velocity signal translates to an inclination-dependent
planetary mass of $M\,\sin\,{i} = 5.81 \pm 0.72~M_J$
\citep[Equation~1]{Torres2008}, a massive giant planet; for sufficiently high
inclinations ($\gtrsim 45^\circ$), the mass of Aldebaran~b may exceed $13~M_J$,
making it a possible low-mass brown dwarf candidate.

@@

>>>>

The stellar oscillations are best fit with a single, low-quality ($Q =
\CombinedQRange{}$) oscillatory mode with $\numax = 2.238^{+ 0.086}_{- 0.080}$
\muHz.  We find no improvement in the marginal likelihood (evidence) or other
model-selection information criteria \citep{Gelman2013} from models with
additional oscillatory modes, so we conclude that the large spacing $\Delta\nu$
is not observable in this data set.  We have determined the stellar properties
of Aldebaran with the additional constraint of \numax determined from this
analysis.  The details of the stellar modelling are presented in Appendix
\ref{sec:mod}.  We have considered the impact of our additional \numax
constraint and run our analysis for different sets of spectroscopic estimates.
For final values we adopt the \citet{2012Sheffield} spectroscopic solution as
being `middle of the road' estimates.  For the analysis without constraint on
\numax we find estimates of the stellar properties as $M = 1.27^{+0.24}_{-0.2}
\, \mathrm{M_{\odot}}$ and age $4.86^{+3.56}_{-2.04} \, \rm Gyr$.  With the
inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and
age $6.38^{+1.42}_{-1.12} \, \rm Gyr$.  It is clear that the addition of \numax
provides substantially more precise estimates of mass and age. With this stellar
mass, the radial velocity signal translates to an inclination-dependent
planetary mass of $M\,\sin\,{i} = 5.81 \pm 0.72~M_J$
\citep[Equation~1]{Torres2008}, a massive giant planet; for sufficiently high
inclinations ($\gtrsim 45^\circ$), the mass of Aldebaran~b may exceed $13~M_J$,
making it a possible low-mass brown dwarf candidate. A recent study by \citet{2018arXiv180105239H} has cast doubt on the validity of the detection of the massive planet $\gamma$~Draconis~b, and by extension similar planets around similar K~giants such as Aldebaran. We remain convinced that Aldebaran~b is a bona fide planet for reasons outlined in Appendix~\ref{gamma_dra}.

@@

\section{The $\gamma$~Draconis Problem is Not a Problem}
\label{gamma_dra}

$\gamma$~Draconis (also known as Eltanin, or $\gamma$~Dra) is a second-magnitude K5III giant which had been observed by \citet{hatzes1993} as part of the same campaign that led to the discovery of Aldebaran~b and Pollux~b. \citet{2018arXiv180105239H} have recently shown that the 702~d period RV variations of the putative Eltanin~b disappeared from 2011-2013, returning in 2014 with a different amplitude and phase. They ascribe this to the beating between two modes of a previously-unidentified kind of stellar variability, and warn that ``Given that the periods found in α Tau are comparable to those in $\gamma$~Dra and both stars are evolved with large radii, a closer scrutiny of the RV variability of $\alpha$~Tau \[Aldebaran\] is warranted.''

For several reasons we are not convinced that this poses an issue for Aldebaran or for K~giant RV planets more generally.
